---
title: "CapstoneProjectYouthfulCities"
author: "AndrewHoward"
date: "November 20, 2015"
output: word_document
---
Welcome to the R Code for my Capstone Project using the Youthful Cities dataset provided by Youthful Cities to Ryerson University for use during the Capstone Project.

For my project I decided to complete several Feature Selection models to help the Youthful Cities team to better understand their data and how their final rankings are impacted by the different features measured.
---
Part 1:
---
Input the data and packages into R and input the city names into the data:
```{r}
data <- read.csv("youthfulcities.csv")
rownames(data) <- c("Accra","Amsterdam","Bangkok","Beirut","Berlin","Bogota","Boston","Beunos Aires","Cairo","Caracas","Casablanca","Chicago","Dallas","Dar Es Salaam","Detroit","Dubai","Durban","Hong Kong","Istanbul","Jakarta","Johannesburg","Karachi","Lagos","Lima","London","Los Angeles","Madrid","Manilla","Mexico City","Miami","Montreal","Moscow","Mumbai","Nairobi","New Dehli","New York City","Osaka","Paris","Quito","Rio De Janerio","Rome","San Fransico","Santiago","Sao Paulo","Seoul","Shanghai","Singapore","Sydney","Tehran","Tel Aviv","Tokyo","Toronto","Vancouver","Warsaw","Washington")
library("DAAG", lib.loc="/Library/Frameworks/R.framework/Versions/3.1/Resources/library")
library("MASS", lib.loc="/Library/Frameworks/R.framework/Versions/3.1/Resources/library")
library("fields", lib.loc="/Library/Frameworks/R.framework/Versions/3.1/Resources/library")
```
---
Part 2:
---
Create a baseline for the analysis using the full feature set:
```{r}
#create a linear model using all of the features possible
full <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
           +Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
#Measure the predictive quality of the modesl to then create the root mean square error baseline for the rest #of the project
basefull <- cv.lm(df=data,full,m=5)
basermse <- sqrt((basefull$cvpred - basefull$OVERALL)^2)/nrow(basefull)
```
----
Part 3:
----
Create a cluster dendogram of the features and cities to illustrate the data:
```{r,echo=FALSE}
#Prep the data by removing unnecessary data
data1 <- data[,-1]
data1 <- data1[,-22]
#Create distance matrixes using euclidean distance
d <- dist(t(data1),method = "euclidean")
e <- dist(data1,method = "euclidean")
#Create heirarchical clustering of the Features and plot the clusters
hc <- hclust(d)
plot(hc, main = "Cluster Dendogram of Features using Euclidean Distance",xlab="Features")
#Add rectangles around the 7 Clusters we would like
rhc <- rect.hclust(hc, k=7)
#Create hierarchical clustering of the cities and plot that aswell
citclu <- hclust(e)
plot(citclu,main = "Cluster Dendogram of Cities using Euclidean Distance",xlab="Cities")
```
This also creates an easy platform to add a heatmap of the data:
```{r,echo=FALSE}
#Make a data matrix of the data so that it can be input into the heatmap function
data_matrix <- data.matrix(data1)
heatmap(data_matrix,Colv=hcd,scale="column")
```
---
Part 3
---
Now I will create a linear model using the Cluster Dendogram of the 7 features from above:
```{r,echo=FALSE}
#Create the linear models using a random feature selected from each of the clusters
clust1 <- lm(OVERALL~Affordability,data=data)
clust3 <- lm(OVERALL~Music,data=data)
clust5 <- lm(OVERALL~Transit,data=data)
clust4 <- lm(OVERALL~Public.space,data=data)
clust2 <- lm(OVERALL~Health,data=data)
clust7 <- lm(OVERALL~Food.and.nightlife,data=data)
clust6 <- lm(OVERALL~Arts,data=data)
#Meausure the predictive quality of each of the models
clust1 <- cv.lm(df=data, clust1, m=5)
rmseclust1 <- sqrt((clust1$cvpred - clust1$OVERALL)^2)/nrow(clust1)
clust2 <- cv.lm(df=data, clust2, m=5)
rmseclust2 <- sqrt((clust2$cvpred - clust2$OVERALL)^2)/nrow(clust2)
clust3 <- cv.lm(df=data, clust3, m=5)
rmseclust3 <- sqrt((clust3$cvpred - clust3$OVERALL)^2)/nrow(clust3)
clust4 <- cv.lm(df=data, clust4, m=5)
rmseclust4 <- sqrt((clust4$cvpred - clust4$OVERALL)^2)/nrow(clust4)
clust5 <- cv.lm(df=data, clust5, m=5)
rmseclust5 <- sqrt((clust5$cvpred - clust5$OVERALL)^2)/nrow(clust5)
clust6 <- cv.lm(df=data, clust6, m=5)
rmseclust6 <- sqrt((clust6$cvpred - clust6$OVERALL)^2)/nrow(clust6)
clust7 <- cv.lm(df=data, clust7, m=5)
rmseclust7 <- sqrt((clust7$cvpred - clust7$OVERALL)^2)/nrow(clust7)
#create a table of the results
rmseclusttab <- cbind(rmseclust1,rmseclust2,rmseclust3,rmseclust4,rmseclust5,rmseclust6,rmseclust7)
#separate the table into 5 Folds for plotting
fivefoldrmseclust<-cbind(colMeans(rmseclusttab[1:11,]),colMeans(rmseclusttab[12:22,]),colMeans(rmseclusttab[23:33,]),colMeans(rmseclusttab[34:44,]),colMeans(rmseclusttab[45:55,]))
#Name each of the features used to show in the plot
rownames(fivefoldrmseclust) <- c("Afford","Health","Music","Pub. Space","Transit","Arts","Food")
#Plot the data and add a red line at the baseline point
boxplotrand <- boxplot(t(fivefoldrmseclust),ylim= c(0.7,2.5), las = 2, ylab="RMSE",main="Mean RMSE on 5 FCV of a Random Feature at 7 the Cluster CutOff")
abline(h=mean(basermse),col="red")
lines(rowMeans(fivefoldrmseclust))
points(rowMeans(fivefoldrmseclust))
```
----
Part 4
----
Experiment 1:

I created a stepwise feature selection model to see the RMSE for each set of features selected:
```{r,echo=FALSE}
#Start with all of the models with one feature added each time
one <- lm(OVERALL~Safety,data=data)
ffold1 <- cv.lm(df=data, one, m=5)
rmse1 <- sqrt((ffold1$cvpred - ffold1$OVERALL)^2)/nrow(ffold1)
two <- lm(OVERALL~Safety+Affordability,data=data)
ffold2 <- cv.lm(df=data, two, m=5)
rmse2 <- sqrt((ffold2$cvpred - ffold2$OVERALL)^2)/nrow(ffold2)
three <- lm(OVERALL~Safety+Affordability+Transit,data=data)
ffold3 <- cv.lm(df=data, three, m=5)
rmse3 <- sqrt((ffold3$cvpred - ffold3$OVERALL)^2)/nrow(ffold3)
four <- lm(OVERALL~Safety+Affordability+Transit+Health,data=data)
ffold4 <- cv.lm(df=data, four, m=5)
rmse4 <- sqrt((ffold4$cvpred - ffold4$OVERALL)^2)/nrow(ffold4)
five <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel,data=data)
ffold5 <- cv.lm(df=data, five, m=5)
rmse5 <- sqrt((ffold5$cvpred - ffold5$OVERALL)^2)/nrow(ffold5)
six <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment,data=data)
ffold6 <- cv.lm(df=data, six, m=5)
rmse6 <- sqrt((ffold6$cvpred - ffold6$OVERALL)^2)/nrow(ffold6)
seven <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment,data=data)
ffold7 <- cv.lm(df=data, seven, m=5)
rmse7 <- sqrt((ffold7$cvpred - ffold7$OVERALL)^2)/nrow(ffold7)
eight <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education,data=data)
ffold8 <- cv.lm(df=data, eight, m=5)
rmse8 <- sqrt((ffold8$cvpred - ffold8$OVERALL)^2)/nrow(ffold8)
nine <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship,data=data)
ffold9 <- cv.lm(df=data, nine, m=5)
rmse9 <- sqrt((ffold9$cvpred - ffold9$OVERALL)^2)/nrow(ffold9)
ten <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space,data=data)
ffold10 <- cv.lm(df=data, ten, m=5)
rmse10 <- sqrt((ffold10$cvpred - ffold10$OVERALL)^2)/nrow(ffold10)
eleven <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services,data=data)
ffold11 <- cv.lm(df=data, eleven, m=5)
rmse11 <- sqrt((ffold11$cvpred - ffold11$OVERALL)^2)/nrow(ffold11)
twelve <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity,data=data)
ffold12 <- cv.lm(df=data, twelve, m=5)
rmse12 <- sqrt((ffold12$cvpred - ffold12$OVERALL)^2)/nrow(ffold12)
thirteen <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access,data=data)
ffold13 <- cv.lm(df=data, thirteen, m=5)
rmse13 <- sqrt((ffold13$cvpred - ffold13$OVERALL)^2)/nrow(ffold13)
fourteen <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music,data=data)
ffold14 <- cv.lm(df=data, fourteen, m=5)
rmse14 <- sqrt((ffold14$cvpred - ffold14$OVERALL)^2)/nrow(ffold14)
fifteen <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music+Arts,data=data)
ffold15 <- cv.lm(df=data, fifteen, m=5)
rmse15 <- sqrt((ffold15$cvpred - ffold15$OVERALL)^2)/nrow(ffold15)
sixteen <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music+Arts+Sports,data=data)
ffold16 <- cv.lm(df=data, sixteen, m=5)
rmse16 <- sqrt((ffold16$cvpred - ffold16$OVERALL)^2)/nrow(ffold16)
seventeen <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music+Arts+Sports+Film,data=data)
ffold17 <- cv.lm(df=data, seventeen, m=5)
rmse17 <- sqrt((ffold17$cvpred - ffold17$OVERALL)^2)/nrow(ffold17)
eightteen <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music+Arts+Sports+Film+Civic.engagement,data=data)
ffold18 <- cv.lm(df=data, eightteen, m=5)
rmse18 <- sqrt((ffold18$cvpred - ffold18$OVERALL)^2)/nrow(ffold18)
nineteen <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife,data=data)
ffold19 <- cv.lm(df=data, nineteen, m=5)
rmse19 <- sqrt((ffold19$cvpred - ffold19$OVERALL)^2)/nrow(ffold19)
twenty <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion,data=data)
ffold20 <- cv.lm(df=data, twenty, m=5)
rmse20 <- sqrt((ffold20$cvpred - ffold20$OVERALL)^2)/nrow(ffold20)
twentyone <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity
               +Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold21 <- cv.lm(df=data, twentyone, m=5)
rmse21 <- sqrt((ffold21$cvpred - ffold21$OVERALL)^2)/nrow(ffold21)
rmsetab <- cbind(rmse1,rmse2,rmse3,rmse4,rmse5,rmse6,rmse7,rmse8,rmse9,rmse10,rmse11,rmse12,rmse13,rmse14,rmse15,rmse16,
                   rmse17,rmse18,rmse19,rmse20,rmse21)
#Find the mean RMSE for each the 5 folds created
fivefoldrmse<-cbind(colMeans(rmsetab[1:11,]),colMeans(rmsetab[12:22,]),colMeans(rmsetab[23:33,]),colMeans(rmsetab[34:44,]),colMeans(rmsetab[45:55,]))
#Name each boxplot and which feature was added at each point
rownames(fivefoldrmse) <- c("Safety","Afford","Transit","Health","Travel","Employ","Enviro","Education"
                            ,"Entrepre","Pub. Space","Financial","Diversity","Digital","Music"
                            ,"Arts","Sports","Film","Civic En.","Food","Fashion","Youth Pop.")
#Plot the data adding a red line for baseline RMSE
boxplot(t(fivefoldrmse),las = 2, ylab="RMSE",main="Mean RMSE on 5 Fold Cross Validation for Stepwise Feature Selection")
abline(h=mean(basermse),col="red")
lines(rowMeans(fivefoldrmse))
points(rowMeans(fivefoldrmse))
```
---
Part 4 and 5:
---
Experiment 2 and 3:

I did the same experiment using 2 different starting points to show the differing results:
```{r,echo=FALSE}
#Experiment 2
one2 <- lm(OVERALL~Music,data=data)
ffold12 <- cv.lm(df=data, one2, m=5)
rmse12 <- sqrt((ffold12$cvpred - ffold12$OVERALL)^2)/nrow(ffold12)
two2 <- lm(OVERALL~Music+Arts,data=data)
ffold22 <- cv.lm(df=data, two2, m=5)
rmse22 <- sqrt((ffold22$cvpred - ffold22$OVERALL)^2)/nrow(ffold22)
three2 <- lm(OVERALL~Music+Arts+Sports,data=data)
ffold32 <- cv.lm(df=data, three2, m=5)
rmse32 <- sqrt((ffold32$cvpred - ffold32$OVERALL)^2)/nrow(ffold32)
four2 <- lm(OVERALL~Music+Arts+Sports+Film,data=data)
ffold42 <- cv.lm(df=data, four2, m=5)
rmse42 <- sqrt((ffold42$cvpred - ffold42$OVERALL)^2)/nrow(ffold42)
five2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement,data=data)
ffold52 <- cv.lm(df=data, five2, m=5)
rmse52 <- sqrt((ffold52$cvpred - ffold52$OVERALL)^2)/nrow(ffold52)
six2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife,data=data)
ffold62 <- cv.lm(df=data, six2, m=5)
rmse62 <- sqrt((ffold62$cvpred - ffold62$OVERALL)^2)/nrow(ffold62)
seven2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion,data=data)
ffold72 <- cv.lm(df=data, seven2, m=5)
rmse72 <- sqrt((ffold72$cvpred - ffold72$OVERALL)^2)/nrow(ffold72)
eight2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold82 <- cv.lm(df=data, eight2, m=5)
rmse82 <- sqrt((ffold82$cvpred - ffold82$OVERALL)^2)/nrow(ffold82)
nine2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+Safety,data=data)
ffold92 <- cv.lm(df=data, nine2, m=5)
rmse92 <- sqrt((ffold92$cvpred - ffold92$OVERALL)^2)/nrow(ffold92)
ten2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
            Safety+Affordability,data=data)
ffold102 <- cv.lm(df=data, ten2, m=5)
rmse102 <- sqrt((ffold102$cvpred - ffold102$OVERALL)^2)/nrow(ffold102)
eleven2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
                Safety+Affordability+Transit,data=data)
ffold112 <- cv.lm(df=data, eleven2, m=5)
rmse112 <- sqrt((ffold112$cvpred - ffold112$OVERALL)^2)/nrow(ffold112)
twelve2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
                Safety+Affordability+Transit+Health,data=data)
ffold122 <- cv.lm(df=data, twelve2, m=5)
rmse122 <- sqrt((ffold122$cvpred - ffold122$OVERALL)^2)/nrow(ffold122)
thirteen2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
                  Safety+Affordability+Transit+Health+Travel,data=data)
ffold132 <- cv.lm(df=data, thirteen2, m=5)
rmse132 <- sqrt((ffold132$cvpred - ffold132$OVERALL)^2)/nrow(ffold132)
fourteen2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
                  Safety+Affordability+Transit+Health+Travel+Employment,data=data)
ffold142 <- cv.lm(df=data, fourteen2, m=5)
rmse142 <- sqrt((ffold142$cvpred - ffold142$OVERALL)^2)/nrow(ffold142)
fifteen2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
        Safety+Affordability+Transit+Health+Travel+Employment+Environment,data=data)
ffold152 <- cv.lm(df=data, fifteen2, m=5)
rmse152 <- sqrt((ffold152$cvpred - ffold152$OVERALL)^2)/nrow(ffold152)
sixteen2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
     Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education,data=data)
ffold162 <- cv.lm(df=data, sixteen2, m=5)
rmse162 <- sqrt((ffold162$cvpred - ffold162$OVERALL)^2)/nrow(ffold162)
seventeen2 <- lm(OVERALL~Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population+
    Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship,data=data)
ffold172 <- cv.lm(df=data, seventeen2, m=5)
rmse172 <- sqrt((ffold172$cvpred - ffold172$OVERALL)^2)/nrow(ffold172)
eightteen2 <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold182 <- cv.lm(df=data, eightteen2, m=5)
rmse182 <- sqrt((ffold182$cvpred - ffold182$OVERALL)^2)/nrow(ffold182)
nineteen2 <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services
               +Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife,data=data)
ffold192 <- cv.lm(df=data, nineteen2, m=5)
rmse192 <- sqrt((ffold192$cvpred - ffold192$OVERALL)^2)/nrow(ffold192)
twenty2 <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion,data=data)
ffold202 <- cv.lm(df=data, twenty2, m=5)
rmse202 <- sqrt((ffold202$cvpred - ffold202$OVERALL)^2)/nrow(ffold202)
twentyone2 <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold212 <- cv.lm(df=data, twentyone2, m=5)
rmse212 <- sqrt((ffold212$cvpred - ffold212$OVERALL)^2)/nrow(ffold212)

rmsetab2 <- cbind(rmse12,rmse22,rmse32,rmse42,rmse52,rmse62,rmse72,rmse82,rmse92,rmse102,rmse112,rmse122,
                  rmse132,rmse142,rmse152,rmse162,rmse172,rmse182,rmse192,rmse202,rmse212)

fivefoldrmse2<-cbind(colMeans(rmsetab2[1:11,]),colMeans(rmsetab2[12:22,]),colMeans(rmsetab2[23:33,]),colMeans(rmsetab2[34:44,]),colMeans(rmsetab2[45:55,]))

rownames(fivefoldrmse2) <- c("Music","Arts","Sports","Film","Civic En.","Food","Fashion","Youth Pop.","Safety","Afford","Transit","Health","Travel","Employ","Enviro","Education"
                             ,"Entrepre","Pub. Space","Financial","Diversity","Digital")

boxplot(t(fivefoldrmse2), las = 2, ylab="RMSE",main="Mean RMSE on 5 Fold Cross Validation for Stepwise Feature Selection
        Experiment 2")
abline(h=mean(basermse),col="red")
lines(rowMeans(fivefoldrmse2))
points(rowMeans(fivefoldrmse2))

#Experiment 3
one3 <- lm(OVERALL~Education,data=data)
ffold13 <- cv.lm(df=data, one3, m=5)
rmse13 <- sqrt((ffold13$cvpred - ffold13$OVERALL)^2)/nrow(ffold13)
two3 <- lm(OVERALL~Education+Entrepreneurship,data=data)
ffold23 <- cv.lm(df=data, two3, m=5)
rmse23 <- sqrt((ffold23$cvpred - ffold23$OVERALL)^2)/nrow(ffold23)
three3 <- lm(OVERALL~Education+Entrepreneurship+Public.space,data=data)
ffold33 <- cv.lm(df=data, three3, m=5)
rmse33 <- sqrt((ffold33$cvpred - ffold33$OVERALL)^2)/nrow(ffold33)
four3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services,data=data)
ffold43 <- cv.lm(df=data, four3, m=5)
rmse43 <- sqrt((ffold43$cvpred - ffold43$OVERALL)^2)/nrow(ffold43)
five3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity,data=data)
ffold53 <- cv.lm(df=data, five3, m=5)
rmse53 <- sqrt((ffold53$cvpred - ffold53$OVERALL)^2)/nrow(ffold53)
six3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access,data=data)
ffold63 <- cv.lm(df=data, six3, m=5)
rmse63 <- sqrt((ffold63$cvpred - ffold63$OVERALL)^2)/nrow(ffold63)
seven3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music,data=data)
ffold73 <- cv.lm(df=data, seven3, m=5)
rmse73 <- sqrt((ffold73$cvpred - ffold73$OVERALL)^2)/nrow(ffold73)
eight3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access
             +Music+Arts,data=data)
ffold83 <- cv.lm(df=data, eight3, m=5)
rmse83 <- sqrt((ffold83$cvpred - ffold83$OVERALL)^2)/nrow(ffold83)
nine3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access
            +Music+Arts+Sports,data=data)
ffold93 <- cv.lm(df=data, nine3, m=5)
rmse93 <- sqrt((ffold93$cvpred - ffold93$OVERALL)^2)/nrow(ffold93)
ten3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access
           +Music+Arts+Sports+Film,data=data)
ffold103 <- cv.lm(df=data, ten3, m=5)
rmse103 <- sqrt((ffold103$cvpred - ffold103$OVERALL)^2)/nrow(ffold103)
eleven3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access
              +Music+Arts+Sports+Film+Civic.engagement,data=data)
ffold113 <- cv.lm(df=data, eleven3, m=5)
rmse113 <- sqrt((ffold113$cvpred - ffold113$OVERALL)^2)/nrow(ffold113)
twelve3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access
              +Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife,data=data)
ffold123 <- cv.lm(df=data, twelve3, m=5)
rmse123 <- sqrt((ffold123$cvpred - ffold123$OVERALL)^2)/nrow(ffold123)
thirteen3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access
                +Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion,data=data)
ffold133 <- cv.lm(df=data, thirteen3, m=5)
rmse133 <- sqrt((ffold133$cvpred - ffold133$OVERALL)^2)/nrow(ffold133)
fourteen3 <- lm(OVERALL~Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access
           +Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold143 <- cv.lm(df=data, fourteen3, m=5)
rmse143 <- sqrt((ffold143$cvpred - ffold143$OVERALL)^2)/nrow(ffold143)
fifteen3 <- lm(OVERALL~Safety+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold153 <- cv.lm(df=data, fifteen3, m=5)
rmse153 <- sqrt((ffold153$cvpred - ffold153$OVERALL)^2)/nrow(ffold153)
sixteen3 <- lm(OVERALL~Safety+Affordability+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold163 <- cv.lm(df=data, sixteen3, m=5)
rmse163 <- sqrt((ffold163$cvpred - ffold163$OVERALL)^2)/nrow(ffold163)
seventeen3 <- lm(OVERALL~Safety+Affordability+Transit+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold173 <- cv.lm(df=data, seventeen3, m=5)
rmse173 <- sqrt((ffold173$cvpred - ffold173$OVERALL)^2)/nrow(ffold173)
eightteen3 <- lm(OVERALL~Safety+Affordability+Transit+Health+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold183 <- cv.lm(df=data, eightteen3, m=5)
rmse183 <- sqrt((ffold183$cvpred - ffold183$OVERALL)^2)/nrow(ffold183)
nineteen3 <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold193 <- cv.lm(df=data, nineteen3, m=5)
rmse193 <- sqrt((ffold193$cvpred - ffold193$OVERALL)^2)/nrow(ffold193)
twenty3 <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold203 <- cv.lm(df=data, twenty3, m=5)
rmse203 <- sqrt((ffold203$cvpred - ffold203$OVERALL)^2)/nrow(ffold203)
twentyone3 <- lm(OVERALL~Safety+Affordability+Transit+Health+Travel+Employment+Environment+Education+Entrepreneurship+Public.space+Financial.Services+Diversity+Digital.access+Music+Arts+Sports+Film+Civic.engagement+Food.and.nightlife+Fashion+Youth.population,data=data)
ffold213 <- cv.lm(df=data, twentyone3, m=5)
rmse213 <- sqrt((ffold213$cvpred - ffold213$OVERALL)^2)/nrow(ffold213)

rmsetab3 <- cbind(rmse13,rmse23,rmse33,rmse43,rmse53,rmse63,rmse73,rmse83,rmse93,rmse103,rmse113,rmse123,rmse133,rmse143,rmse153,rmse163,rmse173,rmse183,rmse193,rmse203,rmse213)

fivefoldrmse3<-cbind(colMeans(rmsetab3[1:11,]),colMeans(rmsetab3[12:22,]),colMeans(rmsetab3[23:33,]),colMeans(rmsetab3[34:44,]),colMeans(rmsetab3[45:55,]))

rownames(fivefoldrmse3) <- c("Education","Entrepre","Pub. Space","Financial","Diversity","Digital","Music"
                            ,"Arts","Sports","Film","Civic En.","Food","Fashion","Youth Pop."
                            ,"Safety","Afford","Transit","Health","Travel","Employ","Enviro")

boxplot(t(fivefoldrmse3), las = 2, ylab="RMSE",main="Mean RMSE on 5 Fold Cross Validation for Stepwise Feature Selection
        Experiment 3")
abline(h=mean(basermse),col="red")
lines(rowMeans(fivefoldrmse3))
points(rowMeans(fivefoldrmse3))
```
